Inferring ecological interactions

### 2016-11-30 index.Rmd
add a makefile for R users that do not use Rstudio

[Dominique Gravel](), [Tim Poisot](), [Kevin Cazelles,]() [Ben Weinstein](benweinstein.weebly.com), [Ignacio Bartomeus](),Ignacio Morales Castilla, David Beauchesne, Mickaël Hedde, Mathilde Besson, Steve Vissault, Guillaume Blanchet

>>>>

[Dominique Gravel](), [Tim Poisot](), [Kevin Cazelles,](http://kevincazelles.fr/) [Ben Weinstein](benweinstein.weebly.com), [Ignacio Bartomeus](),Ignacio Morales Castilla, David Beauchesne, Mickaël Hedde, Mathilde Besson, Steve Vissault, Guillaume Blanchet
